---
title: "ggpage features"
author: "Emil Hvitfeldt"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ggpage features}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Variable paragraph length

The `ggpage` package allows for variable length of paragraphs if the text doesn't hold information regarding paragraphs. This is done by supplying the `variable.paragraph.length` argument in `ggpage_build` with a function that generate random natural numbers. Such as the `rpois` function.

```{r, message=FALSE}
library(magrittr)
library(dplyr)
library(ggpage)


book <- tinderbox %>%
  tidytext::unnest_tokens(text, text)

ggpage_build(book, para.fun = rpois, lambda = 75) %>%
  ggpage_plot()
ggpage_build(book, para.fun = rpois, lambda = 75) %>%
  ggpage_plot()
ggpage_build(book, para.fun = rpois, lambda = 500) %>%
  ggpage_plot()
ggpage_build(book, para.fun = rpois, lambda = 500) %>%
  ggpage_plot()
```

## Show paper

With the newest update `ggpage` allows you to draw a rectangle around each "page". 

```{r}
ggpage_build(tinderbox) %>%
  ggpage_plot(paper.show = TRUE)
```

It allows you use specify a color both as a constant,

```{r}
ggpage_build(tinderbox) %>%
  ggpage_plot(paper.show = TRUE, paper.color = "pink")
```

or by a string of colors. In this case a faded rainbow.

```{r}
ggpage_build(tinderbox) %>%
  ggpage_plot(paper.show = TRUE, paper.color = rainbow(9), paper.alpha = 0.3)
```

## Show page number

It can be hard to see the order of the pages in the standard vizualization. However it is possible to add a page number in the sides or corners of each page.

```{r}
directions <- c("top", "top-right", "right", "bottom-right", "bottom",
                "bottom-left", "left", "top-left")
ggpage_build(tinderbox) %>%
  ggpage_plot(page.number = directions[1])
ggpage_build(tinderbox) %>%
  ggpage_plot(page.number = directions[2])
ggpage_build(tinderbox) %>%
  ggpage_plot(page.number = directions[3])
ggpage_build(tinderbox) %>%
  ggpage_plot(page.number = directions[4])
ggpage_build(tinderbox) %>%
  ggpage_plot(page.number = directions[5])
ggpage_build(tinderbox) %>%
  ggpage_plot(page.number = directions[6])
ggpage_build(tinderbox) %>%
  ggpage_plot(page.number = directions[7])
ggpage_build(tinderbox) %>%
  ggpage_plot(page.number = directions[8])

```

## Variable page length

The package also support a variable page length. This can be helpful when a collection of smaller texts are considered in the same vizualisation such as tweets.

```{r}
tinderbox %>%
  mutate(short = ceiling(seq_len(nrow(tinderbox)) / 10)) %>%
  ggpage_build(page.col = "short", lpp = 10) %>%
  ggpage_plot()
```

## Centering

`ggpage` now supports left, right and both-sided alignments.

```{r}
ggpage_build(tinderbox, align = "right") %>%
  ggpage_plot()

ggpage_build(tinderbox, align = "both") %>%
  ggpage_plot()
```

## Paragraph to line

Lastly for convience does `ggpage` include a way to transform a data.frame with paragraph tokens to a data.frame with line tokens.

```{r}
nest_paragraphs(data = tinderbox_paragraph, input = text) %>%
  head()

nest_paragraphs(tinderbox_paragraph, text, width = 40) %>%
  head()
```





